---
title: "notes"
output: html_document
---

```{r setup, include=FALSE,echo = F, message=F, warning=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
load(paste0(getwd(),"/all_data.Rdata"))
require(knitr)
require(markdown)
```


## Data Summary

```{r, echo =F}
plot.na(df2)
```

NA pattern unclear.

# Part I. Examination of Q8 "relaxing and playing games how often do you use social network sites to"
## Part Ia. PCA and FA

Principal component analysis of q8 is adequate due to the 7 step scale of the answers. Normality assumption ont meat, but also not required. PCA applied to cleaned q8 with missing values removed.
```{r,results='hide',fig.align='center'}
screeplot(prcomp(q8nonanum),main="Principal components for Q8")
```

An automated procedure performs factor analysis on q8 by examining different number of factors based, partly on the PCA, and excludes those who do not pass significance. 2 factor decomposition does not pass and hence the hypothesis that Question8 can be viewed as a "socializing" vs "alone" question is rejected. The higher the correlation the brighter the color.

```{r, fig.align='center',fig.widt=4,fig.height=4}
par(oma=.pardefault$oma + c(0,8,0,0))
plot.matrix(factanal(q8nonanum,3),col=grey.colors(10))
plot.matrix(factanal(q8nonanum,4),col=grey.colors(10))
```

The 3 factor analysis groups as follows:

* Download music + play games with friends + being entertained
* browsing for no reason + overcoming loneliness (+ releasing tension)
* playing games alone

The 4 factor analysis is essentially the same as the 3 factor wit the addition of a 4th factor mostly representing "releasing tension".

## Part Ib. Q8 ~ Q7
### Predicting Q7 with Q8

Thourough model inspection coming soon...

```{r,echo=F}
print(q8predq7accuracy)
```

### Predicting Q7 with Q8_PCA
