---
title: "notes"
output: html_document
---

```{r setup, include=FALSE,echo = F, message=F, warning=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
load(paste0(getwd(),"/all_data.Rdata"))
require(knitr)
require(markdown)
```


## Data Summary

```{r, echo =F,fig.align='center'}
# plot.na(df2)
```

NA pattern unclear.

# Part I. Examination of Q8 "relaxing and playing games how often do you use social network sites to"
## Part Ia. PCA

Principal component analysis of q8 is adequate due to the 7 step scale of the answers. Normality assumption ont meat, but also not required. PCA applied to cleaned q8 with missing values removed.
```{r,results='hide',fig.align='center'}
my.barplot(prcomp(q8nonanum)$sdev^2,main="Principal components for Q8",namez=names(q8nonanum))
```

## Part Ib. FA

Factor analysis on Q8. Similar results for varimax and promax. The groupings are:

* Factor1 (Games): playgamesfriends, plagamesstranger, playgamesalone
* Factor2 (Spare time): killtime, browsenoreason, beentertained
* Factor3: realeasetension, overcomelone

Downloadmusic appears to be unrelated to the 3 identified above latent variables.

```{r, echo=F}
print(q8fa$`3factors`, cutoff = .4, sort = T)
print(q8fa1, cutoff = .3, sort = T)
```

## Part Ic. FA on Q8 and Q7

Downloadmusic still appears independent. At a .3 cutoff some mixtures occur:
```{r, echo = F, fig.align = 'center'}
par(mfrow=c(2,2), mar = .pardefault$mar - c(2,-3,2,2))
plot.matrix(q7q8fa1, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa2, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa3, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa4, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
```

## Part Id. CLM Q8 ~ Q7
```{r}
dim(q7q8nona)
```
Hence, pca predictors are requried. PCA of Q7 used in combination


# Part II. FA Q10

Minimum 3 factors required. 4 factors are too many.

```{r}
par(mar = .pardefault$mar + c(0,5,0,0))
plot.matrix(q10fa, cutoff = .5, main = "Q10 FA, cutoff .5", col = grey.colors(2))
```


## Part II. Q10 vs Q11, Q10 vs Q19, Q10 vs Q20


# Part III. proper analysis of q19