---
title: "SNS Survey Analysis Notes 2"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup, include=FALSE,echo = F, message=F, warning=F}
require(knitr)
require(psych)
require(markdown)
require(xtable)
require(ordinal)

knitr::opts_chunk$set(echo = F, message=F, warning=F)
load(paste0(getwd(),"/all_data.Rdata"))
load(paste0(getwd(),"/bucket.Rdata"))
load(paste0(getwd(),"/.Rdata"))
source("Rfunctions/Rfunctions.R")
```

# Summary

# Internal consistency
Internal consistency via Chronbach's alpha on scale questions. Only meaningful for one "dimensional" scales, i.e. sacles measuring one attribute. Each plot displays the raw Chronebach $\alpha$ for the given data set with all variables present. The bars marked in dark grey are the dropped variables. On top of each plot is drawn the uniqueness of each variable extracted from a factor analysis with the respective number of factors. The test is performed recursively until dropping more variables yields no further improvement. The sequence of variable names preceeding each plot is the order in which variables are dropped (if any) and the change in raw $\alpha$.

--

## Q10

No variables dropped

```{r,fig.align='center'}
q10alpha = alpha.recursive(q10nonanum)
dropped = !names(q10nonanum) %in% names(q10alpha)
names(q10nonanum)[dropped]

q10alpha2 = alpha(q10nonanum)
b = my.barplot(q10alpha2$alpha.drop$raw_alpha,ylim=c(0,1),col = grey((!dropped)*.3+.4),
               namez = rownames(q10alpha2$alpha.drop),main="Q10",ylab=expression(alpha))
lines(as.vector(b),q10fa$uniquenesses,col=2,lwd=2) #,axes=F,ann=F
legend(x=my.par("below",.1)$x,y=my.par("below",.1)$y,fill=c(grey(.4),2),
       c("Dropped","FA3 uniqueness"),xpd=NA,horiz=T,bty="n",xjust=.5)
```

## Q19

isel8 "If I had to go out of town for a few weeks, it would be difficult to find someone who would look after my house or apartment (the plants, pets, garden, etc.)"

isel12 "If I needed some help in moving to a new house or apartment, I would have a hard time finding someone to help me. "

```{r,fig.align='center',results='markup'}
q19alpha = alpha.recursive(q19nonanum)
dropped = !names(q19nonanum) %in% names(q19alpha)
names(q19nonanum)[dropped]

q19alpha2 = alpha(q19nonanum)
b = my.barplot(q19alpha2$alpha.drop$raw_alpha,ylim=c(0,1),col = grey((!dropped)*.3+.4),
               namez = rownames(q19alpha2$alpha.drop),main="Q19",ylab=expression(alpha))
lines(as.vector(b),q19fa2$uniquenesses,col=2,lwd=2) #,axes=F,ann=F
lines(as.vector(b),q19fa3$uniquenesses,col=3,lwd=2) #,axes=F,ann=F
lines(as.vector(b),q19fa4$uniquenesses,col=4,lwd=2) #,axes=F,ann=F
legend(x=my.par("below",.1)$x,y=my.par("below",.1)$y,fill=c(grey(.4),2:4),
       c("Dropped","FA2 uniqueness","FA3 uniqueness","FA4 uniqueness"),xpd=NA,horiz=T,bty="n",xjust=.5)
```

## Q20

bridge4 "Based on the poeple I interact with, it is easy for me to hear about new job opportunities"

```{r,fig.align='center',results='markup'}
q20alpha = alpha.recursive(q20nonanum)
dropped = !names(q20nonanum) %in% names(q20alpha)
names(q20nonanum)[which(dropped)]

q20alpha2 = alpha(q20nonanum)
b = my.barplot(q20alpha2$alpha.drop$raw_alpha,ylim=c(0,1),col = grey((!dropped)*.3+.4),
               namez = rownames(q20alpha2$alpha.drop),main="Q20",ylab=expression(alpha))
lines(as.vector(b),q20fa2$uniquenesses,col=2,lwd=2) #,axes=F,ann=F
lines(as.vector(b),q20fa3$uniquenesses,col=3,lwd=2) #,axes=F,ann=F
lines(as.vector(b),q20fa4$uniquenesses,col=4,lwd=2) #,axes=F,ann=F
legend(x=my.par("below",.1)$x,y=my.par("below",.1)$y,fill=c(grey(.4),2:4),
       c("Dropped","FA2 uniqueness","FA3 uniqueness","FA4 uniqueness"),xpd=NA,horiz=T,bty="n",xjust=.5)
```

---

# Relations with demographic data

Below are shown some cumulative link models, which attempt to explain each variables from the respective question via the demographic data. Thus, in the subsection are listed models for the sub questions. Only models which have paased validation are shown.

## Q10


```{r}
print.this(m0)
```

## Q12

```{r}
print.this(m2)
```



## Q15

```{r}
print.this(m4)
```

## Q16

```{r}
print.this(m5)
```

## Q18

q18.1_lifesat1 "In most ways my life is close to my ideal"

```{r}
print.this(m6)
```

## Q20

q20.3_bridge3 "Interacting with people makes me want to try new things"

q20.5_bridge5 "Interacting with people makes me interested in things that happen outside of my town"

q20.7_bridge7 "I come in contact with new people all the time"

```{r}
print.this(m8)
```












