---
title: "notes"
output: html_document
---

```{r setup, include=FALSE,echo = F, message=F, warning=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
load(paste0(getwd(),"/all_data.Rdata"))
require(knitr)
require(markdown)
```


## Data Summary


NA pattern unclear.

# Part I. Examination of Q8 "relaxing and playing games how often do you use social network sites to"

## Part Ia. PCA

Principal component analysis of q8 is adequate due to the 7 step scale of the answers. Normality assumption ont meat, but also not required. PCA applied to cleaned q8 with missing values removed.

```{r,results='hide',fig.align='center'}
# my.barplot(prcomp(q8nonanum)$sdev^2,main="Principal components for Q8",namez=names(q8nonanum))
```

## Part Ib. Q8 FA

3, 4 and 5 factors are acceptable. Shown are only 3 and 4 factors, as 5 appear too many for 9 variables.

```{r, echo=F,fig.align='center'}
par(mfrow=c(1,2), mar = .pardefault$mar + c(0,2,0,2))
plot.matrix(q8fa3, cutoff=.4,main="Q8fa3, cutoff = .4",col = grey.colors(2))
plot.matrix(q8fa4, cutoff=.4,main="Q8fa3, cutoff = .4", col = grey.colors(2))
```

* Factor1 (Games): playgamesfriends, plagamesstranger, playgamesalone
* Factor2 (Spare time): killtime, browsenoreason, beentertained
* Factor3: realeasetension, overcomelone

Downloadmusic appears to be unrelated to the 3 identified above latent variables.



```{r, echo=F,fig.align='center'}
par(mfrow=c(1,2), mar = .pardefault$mar - c(0,2,0,2))
my.barplot(q8fa3$uniquenesses,namez = names(q8fa3$uniquenesses),main="Unique variance")
my.barplot(q8fa4$uniquenesses,namez = names(q8fa4$uniquenesses),main="Unique variance")

```

## Part Ic. FA on Q8 and Q7

Downloadmusic still appears independent. At a .3 cutoff some mixtures occur:
```{r, echo = F, fig.align = 'center'}
par(mfrow=c(2,2), mar = .pardefault$mar - c(2,-3,2,2))
plot.matrix(q7q8fa1, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa2, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa3, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
plot.matrix(q7q8fa4, cutoff = .3, main = "Cutoff .3", col = grey.colors(2))
```


# Part II. FA Q10

Minimum 3 factors required. 4 factors are too many.

```{r,fig.align='center'}
par(mar = .pardefault$mar + c(-2,4,-3,-2), mfrow=c(2,1))
plot.matrix(q10fa,cutoff=.33,col=grey.colors(2),main="Cutoff .33")
my.barplot(q10fa$uniquenesses,namez=names(q10fa$uniquenesses),main = "Unique variance")
```


# Part III. proper analysis of q19
Acceptable factors are 2 to 7.

```{r, fig.align='center'}

```

# Part IV. proper analysis of q20



```{r, fig.align='center'}
par(mar = .pardefault$mar + c(-2,4,-3,-2), mfrow=c(2,1))
plot.matrix(q10q11fa$`3factors`,cutoff=.35,col=grey.colors(2),main="Cutoff .35")
my.barplot(q10q11fa$`3factors`$uniquenesses,
           namez=names(q10q11fa$`3factors`$uniquenesses),main = "Unique variance")
```

## Part X. Q10 vs Q19, Q10 vs Q20
## Part II. Q10 vs Q11
FA points towards 3 factors. 4 factors identify Q11 as a separate factor.


